The Deviation of China Map as a Regression Problem

### 2013-10-04 paper.tex
add gmap evaluation

\title{The Deviation of China Map as a Regression Problem}
\author{Wu Yongzheng}

@@

\section{The Problem}

@@

Figure~\ref{fig:fxy-degree}(left) shows the plot, $f_x(110.16,y)$. The curve
looks like a second order curve, but if we go that direction, it's going to be
very tough.
It is a lot simpler if we measure the deviation in meters rather
than degrees.

@@

To check their correctness, we can compute a deviated coordinate and check
whether it aligns with the deviated map.
We now compute the deviated coordinate of the Monument to the People's Heroes
using its true coordinate $(116.391667,39.903056)$.
$f_x(116.391667,39.903056)=531.91$ meters and
$f_y(116.391667,39.903056)=155.39$ meters.
This means that the deviated coordinate is 531.91 meters to the east and 155.39
to the north.
We then convert meters into degrees and adds them to the true coordinate.

@@

We now put the deviated coordinate in a deviated map as in
Figure~\ref{fig:map-jjmdd}.  It aligns nicely.

>>>>

\title{The Deviation of China Map as a Regression Problem}
\author{Wu Yongzheng}
\date{}

@@

\section{Introduction}

@@

Figure~\ref{fig:fxy-degree}(left) shows the plot, $f_x(110.16,y)$. The curve
looks like a second order curve, but if we go that direction, it's going to be
very tough.
It is a lot simpler if we measure the deviation in meters rather
than degrees.
Note that earth's radius is 6378137 meters in Google Map.
I didn't know this until the experiment was all finished.
However, this shouldn't cause any error even if I set the radius to 1 meter,
because in the end, meters is converted back to degrees and the error cancels.

@@

\section{Evaluation}

To check their correctness, we can compute a deviated coordinate and check
whether it aligns with the deviated map.
We now compute the deviated coordinate of the Monument to the People's Heroes
using its true coordinate $(116.391667,39.903056)$.\footnote{
I cannot find any authoritative location of the monument.
The one that I use is from Wikipedia.
}
$f_x(116.391667,39.903056)=531.91$ meters and
$f_y(116.391667,\allowbreak{}39.903056)=155.39$ meters.
This means that the deviated coordinate is 531.91 meters to the east and 155.39
to the north.
We then convert meters into degrees and adds them to the true coordinate.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.6\textwidth]{gmapsat.png}
\end{center}
\caption{The monument's true coordinate in GMap's satellite image}
\label{fig:gmapsat}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.6\textwidth]{gmapstr.png}
\end{center}
\caption{The monument's deviated coordinate in GMap's street map}
\label{fig:gmapstr}
\end{figure}

The green arrow in Figure~\ref{fig:gmapsat} shows the true coordinate in the
Google Maps' satellite image.  Figure~\ref{fig:gmapstr} shows the deviated
coordinate in the Google Maps' street map.
The red balloon, which is the nearest landmark, should be ignored.
The green arrows in both maps are slightly to the southeast of the monument
center, but as long as they offset the same amount, it is as good.
